Inference of proto-neutron star properties from gravitational wave data in core-collapse supernovae.

### 2020-09-30 results.tex
add ref+update text

The same analysis has been performed using expected sensitivity curves for the third generation of
gravitational wave detectors. The US based project Cosmic Explorer~\cite{} is proposing to reach out
its design sensitivity circa 2040 through two phases labeled CE1 and CE2 also shown in
Figure~\ref{fig:spectrum}. In Europe, the Einstein Telescope is composed of three nested interferometers
in a configuration of an equilateral triange~\cite{}.

@@

\hline
\multirow{3}{*}{aLIGO} & $d_{r}$ & 7   & 27  & 24  & 22  & 16  & 10  & 37  & 45 \\
\cline{2-10}
                       & $d_{det}$ & 11 & 36 & 26 & 27 & 21 & 16 & 74 & 61\\
                       & SNR      & 14 & 46 & 33 & 35 & 27 & 21 & 96 & 80\\

\hline
\hline
\multirow{3}{*}{ADV}   & $d_{r}$ & 6   & 25  & 20  & 19  & 14  & 10  & 43  & 42 \\
\cline{2-10}
                       & $d_{det}$ &  &  &  &  &  &  &  & \\
                       & SNR      &  &  &  &  &  &  &  & \\

\hline
\hline
\multirow{2}{*}{CE1}   & $d_{r}$   & 79  & 303 & 257 & 229 & 186 & 115 & 523 & 490 \\
\cline{2-10}
                       & $d_{det}$ & 115 & 377 & 270 & 282 & 217 & 168 & 774  & 633\\
                       & SNR      & 149 & 490 & 352 & 366 & 282 & 218 & 1006 & 822\\

\hline
\multirow{2}{*}{CE2}   & $d_{r}$  & 135 & 518 & 464 & 405 & 305 & 183 & 391 & 700 \\
\cline{2-10}
                       & $d_{det}$ & 197 & 649 & 468 & 489 & 375 & 294 & 1347  & 1100\\
                       & SNR    & 256 & 843 & 608 & 635 & 487 & 382 & 1751 & 1430\\

\hline
\multirow{2}{*}{ET\_B} & $d_{r}$ & 71  & 293 & 248 & 245 & 158 & 123 & 113 & 392 \\
\cline{2-10}
                       & $d_{det}$ & 106 & 364 & 274 & 391 & 216 & 200 & 805 & 665\\
                       & SNR      & 138 & 473 & 356 & 379 & 381 & 260 & 1046 & 865\\

\hline
\multirow{2}{*}{ET\_C} & $d_{r}$ & 75  & 302 & 239 & 237 & 172 & 131 & 239 & 446 \\
\cline{2-10}
                       & $d_{det}$ & 97 & 332 & 246 & 260 & 194 & 164 & 727  & 603\\
                       & SNR      & 126 & 432 & 320 & 338 & 252 & 213 & 945 & 783\\

\hline
\multirow{2}{*}{ET\_D} & $d_{r}$ & 83  & 329 & 257 & 261 & 186 & 139 & 369 & 523 \\
\cline{2-10}
                       & $d_{det}$ & 107 & 368 & 271 & 285 & 213 & 174 & 796  & 661\\
                       & SNR      & 140 & 477 & 352 & 371 & 277 & 227 & 1034 & 859 \\

  \end{tabular}
  \caption{%%
    Maximal distance $d_{max}$ at which the ratio $r=M_{\rm PNS}/R_{\rm PNS}^2$ is reconstructed
    with good accuracy for a source optimally oreinted with respect to the GW detectors
    considered in this study.
    Matched filter signal-to-noise ratio (SNR) of the simulated waveforms for
    the different GW detectors. The source is located at 10 kpc and is optimally oriented
    with respect to the detector.
    %%
  }
  \label{tab:results}
\end{table}

>>>>

The same analysis has been performed using expected sensitivity curves for the third generation of
gravitational wave detectors. The US based project Cosmic Explorer~\cite{reitze2019cosmic} is proposing
to reach out its design sensitivity circa 2040 through two phases labeled CE1 and CE2 also shown in
Figure~\ref{fig:spectrum}. In Europe, the Einstein Telescope is composed of three nested interferometers
in a configuration of an equilateral triange~\cite{Hild_2011}.

@@

\hline
\multirow{3}{*}{aLIGO} & $d_{r}$ & 7   & 27  & 24  & 22  & 16  & 10  & 37  & 45 \\
\cline{2-10}
                       & $d_{det}$ & 11 & 36 & 26 & 27 & 21 & 16 & 74 & 61\\
%                       & SNR      & 14 & 46 & 33 & 35 & 27 & 21 & 96 & 80\\

\hline
\hline
\multirow{3}{*}{ADV}   & $d_{r}$ & 6   & 25  & 20  & 19  & 14  & 10  & 43  & 42 \\
\cline{2-10}
                       & $d_{det}$ &  &  &  &  &  &  &  & \\
%                       & SNR      &  &  &  &  &  &  &  & \\

\hline
\hline
\multirow{2}{*}{CE1}   & $d_{r}$   & 79  & 303 & 257 & 229 & 186 & 115 & 523 & 490 \\
\cline{2-10}
                       & $d_{det}$ & 115 & 377 & 270 & 282 & 217 & 168 & 774  & 633\\
%                       & SNR      & 149 & 490 & 352 & 366 & 282 & 218 & 1006 & 822\\

\hline
\multirow{2}{*}{CE2}   & $d_{r}$  & 135 & 518 & 464 & 405 & 305 & 183 & 391 & 700 \\
\cline{2-10}
                       & $d_{det}$ & 197 & 649 & 468 & 489 & 375 & 294 & 1347  & 1100\\
%                       & SNR    & 256 & 843 & 608 & 635 & 487 & 382 & 1751 & 1430\\

\hline
\multirow{2}{*}{ET\_B} & $d_{r}$ & 71  & 293 & 248 & 245 & 158 & 123 & 113 & 392 \\
\cline{2-10}
                       & $d_{det}$ & 106 & 364 & 274 & 391 & 216 & 200 & 805 & 665\\
%                       & SNR      & 138 & 473 & 356 & 379 & 381 & 260 & 1046 & 865\\

\hline
\multirow{2}{*}{ET\_C} & $d_{r}$ & 75  & 302 & 239 & 237 & 172 & 131 & 239 & 446 \\
\cline{2-10}
                       & $d_{det}$ & 97 & 332 & 246 & 260 & 194 & 164 & 727  & 603\\
%                       & SNR      & 126 & 432 & 320 & 338 & 252 & 213 & 945 & 783\\

\hline
\multirow{2}{*}{ET\_D} & $d_{r}$ & 83  & 329 & 257 & 261 & 186 & 139 & 369 & 523 \\
\cline{2-10}
                       & $d_{det}$ & 107 & 368 & 271 & 285 & 213 & 174 & 796  & 661\\
%                       & SNR      & 140 & 477 & 352 & 371 & 277 & 227 & 1034 & 859 \\

  \end{tabular}
  \caption{%%
    Maximal distance $d_{r}$ at which the ratio $r=M_{\rm PNS}/R_{\rm PNS}^2$ is reconstructed
    with good accuracy for a source optimally oreinted with respect to the GW detectors
    considered in this study. $d_{det}$ is the distance at which one could detect a source
    optimally oriented with a matched filter signal-to-noise ratio of 13 in the  different
    GW detectors.
    %%
  }
  \label{tab:results}
\end{table}
